True Stellar Obliquity Distribution of Exoplanets

### 2022-11-18 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure}[ht!]
    \script{hbm.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/hbm.pdf}
        \caption{Hierarchical Bayesian model to infer \emph{true} stellar obliquity for planets with $i_{\star}$ inferred from their rotation periods.}
        \label{fig:hbm}
    \end{centering}
\end{figure}

@@

\begin{figure*}[ht!]
    \script{dist.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/dist.pdf}
        \caption{$\cos{\psi}$ distributions for the sample with $i_\star$ measured and all planets.}
        \label{fig:dist}
    \end{centering}
\end{figure*}

@@

\begin{figure*}[ht!]
    \script{teff_cut.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/teff_cut.pdf}
        \caption{$\cos{\psi}$ distributions for the $i_\star$ sample including/not including $>$7000 K stars.}
        \label{fig:teff_cut}
    \end{centering}
\end{figure*}

@@

\begin{figure*}[ht!]
    \script{rand_inc.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/rand_inc.pdf}
        \caption{$\cos{\psi}$ distributions for the $i_\star$ sample with/without informative $i_\star$ priors.}
        \label{fig:rand_inc}
    \end{centering}
\end{figure*}

@@

\begin{figure*}[ht!]
    \script{bootstrap.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/bootstrap.pdf}
        \caption{$\cos{\psi}$ distributions for the $i_\star$ sample with/without informative $i_\star$ priors.}
        \label{fig:bootstrap}
    \end{centering}
\end{figure*}

>>>>

\begin{figure}[ht!]
    \script{hbm.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/hbm.pdf}
        \caption{Hierarchical Bayesian framework to infer stellar obliquity distribution described by hyperparameters $\theta$ from individual system's stellar obliquity $\psi_n$. $\psi_n$ is calculated by the system's sky-projected stellar obliquity $\lambda_n$ and stellar inclination $i_{\star, n}$.}
        \label{fig:hbm}
    \end{centering}
\end{figure}

@@

% \begin{figure*}[ht!]
%     \script{dist.py}
%     \begin{centering}
%         \includegraphics[width=\linewidth]{figures/dist.pdf}
%         \caption{$\cos{\psi}$ distributions for the sample with $i_\star$ measured and all planets.}
%         \label{fig:dist}
%     \end{centering}
% \end{figure*}

@@

% \begin{figure*}[ht!]
%     \script{teff_cut.py}
%     \begin{centering}
%         \includegraphics[width=\linewidth]{figures/teff_cut.pdf}
%         \caption{$\cos{\psi}$ distributions for the $i_\star$ sample including/not including $>$7000 K stars.}
%         \label{fig:teff_cut}
%     \end{centering}
% \end{figure*}

@@

% \begin{figure*}[ht!]
%     \script{rand_inc.py}
%     \begin{centering}
%         \includegraphics[width=\linewidth]{figures/rand_inc.pdf}
%         \caption{$\cos{\psi}$ distributions for the $i_\star$ sample with/without informative $i_\star$ priors.}
%         \label{fig:rand_inc}
%     \end{centering}
% \end{figure*}

@@

% \begin{figure*}[ht!]
%     \script{bootstrap.py}
%     \begin{centering}
%         \includegraphics[width=\linewidth]{figures/bootstrap.pdf}
%         \caption{$\cos{\psi}$ distributions for the $i_\star$ sample with/without informative $i_\star$ priors.}
%         \label{fig:bootstrap}
%     \end{centering}
% \end{figure*}
